MaxEnt: What is it good for?

### 2015-07-02 ms.tex
Nine possibilities instead of 10

@@

As an example, let's update the prior from Figure~\ref{fig:distribution}
using the testable information $\left<(x - 5)^2\right>_p = 1$. The appropriate
value of the lagrange multiplier is $\lambda=0.5163846$, and the posterior is
shown in Figure~\ref{fig:distribution3}.
\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{distribution3.pdf}
\caption{\label{fig:distribution3}}
\end{center}
\end{figure}

>>>>

Throughout this paper, we will look at examples of MaxEnt updating from a prior
$q(x)$ to a posterior $p(x)$ in different situations where the available
information takes different forms. The prior distribution for all of the
examples is a discrete prior over nine possible values of $x$, and is shown
in Figure~\ref{fig:distribution}.

@@

As an example, let's update the prior from Figure~\ref{fig:distribution}
using the testable information $\left<(x - 5)^2\right>_p = 1$. The appropriate
value of the lagrange multiplier is $\lambda=0.516375$, and the posterior is
shown in Figure~\ref{fig:distribution3}.
\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{distribution3.pdf}
\caption{\label{fig:distribution3}}
\end{center}
\end{figure}
